MapReduce to My Ears\\ {\Large Using Big Data for Music Synthesis}

### 2013-05-10 writeup/paper.tex
fixing TeX

One might describe our final piece, \emph{Digital Nightmare}, as an unrelenting flood of almost patternless musical information.
This characteristic emerges from some simplifications in design choices that a later vernon of our process would look to address.
Here we present a list of such areas and possible solutions.
\begin{itemized}
\item Each instrument plays a note during every musical time unit (beat). This results in constant note information without any space for the listener to "catch up".  Darker colors below some threshold of brightness could all be translated into musical rests.
\item Each note played last only one beat, i.e quarter notes are the only length note used.  Consecutive image regions with similar colors could be "strung together" cause some instruments to play longer notes.
\item Late on in the process, we moved from saturation mapping to velocity to choosing a fixed velocity of 127.  We found that velocity dynamics were not so perceptible with the degree of musical production we were willing to invest.  Spending more time in the post-processing phase and focusing on musical dynamics such as volume, panning, etc could improve the contribution of velocity to a musical piece.
\item In out final piece, saturation did not contribute to velocity, but instead was a component of the octave calculation. This choice was made after observing some short musical pieces and feeling that the color to sound mapping was not as intuitive as we had expected.  This change helped somewhat, but we feel the issue was related to a number of factors including the limitations of the HSB color model to represent the human visual model, the discretization of a continuous range (color is continuous whereas music notes are discrete), and using a constant scale rather than a logarithmic scale to represent musical frequencies (which are inherently logarithmic, each an octave higher is twice the lower octave's frequency).
\end{itemized}

@@

At the onset of this project, we had a vision for translating images in music and we have succeeded in doing so.
Just about every design decision in our process has room for improvement, we are pleased to have at least found a path from start to finish, though not without trials.
At every stage of the pipeline, there were new complexities to discover - the various color models and their relationships, the difficulty in using natural language to discuss color, or the vast number of parameters needed for machines to represent a piece of audio or visual art. 
However challenging though, the journey has put into perspective the amazing ability of the painter and composer to produce works of art with far more complexity than machines can manage. 
We hope that our work inspires technologists to apply their skills to reinterpret works of others from unrelated fields, and vice versa.

>>>>

One might describe our final piece, \emph{Digital Nightmare}, as an unrelenting flood of almost patternless musical information.
This characteristic emerges from some simplifications in design choices that a later vernon of our process would look to address.
Here we present a list of such areas and possible solutions.

\begin{itemize}

\item Each instrument plays a note during every musical time unit
  (beat). This results in constant note information without any space
  for the listener to "catch up".  Darker colors below some threshold
  of brightness could all be translated into musical rests.

\item Each note played last only one beat, i.e quarter notes are the
  only length note used.  Consecutive image regions with similar
  colors could be "strung together" cause some instruments to play
  longer notes.

\item Late on in the process, we moved from saturation mapping to
  velocity to choosing a fixed velocity of 127.  We found that
  velocity dynamics were not so perceptible with the degree of musical
  production we were willing to invest.  Spending more time in the
  post-processing phase and focusing on musical dynamics such as
  volume, panning, etc could improve the contribution of velocity to a
  musical piece.

\item In our final piece, saturation did not contribute to velocity,
  but instead was a component of the octave calculation. This choice
  was made after observing some short musical pieces and feeling that
  the color to sound mapping was not as intuitive as we had expected.
  This change helped somewhat, but we feel the issue was related to a
  number of factors including the limitations of the HSB color model
  to represent the human visual model, the discretization of a
  continuous range (color is continuous whereas music notes are
  discrete), and using a constant scale rather than a logarithmic
  scale to represent musical frequencies (which are inherently
  logarithmic, each an octave higher is twice the lower octave's
  frequency).

\end{itemize}

@@

At the onset of this project, we had a vision for translating images
in music and we have succeeded in doing so.  Just about every design
decision in our process has room for improvement, we are pleased to
have at least found a path from start to finish, though not without
trials.  At every stage of the pipeline, there were new complexities
to discover --- the various color models and their relationships, the
difficulty in using natural language to discuss color, or the vast
number of parameters needed for machines to represent a piece of audio
or visual art.  However challenging though, the journey has put into
perspective the amazing ability of the painter and composer to produce
works of art with far more complexity than machines can manage.  We
hope that our work inspires technologists to apply their skills to
reinterpret works of others from unrelated fields, and vice versa.
